\bf Classification and Regression on Random Dot Product Graphs

### 2024-03-22 draft.Rmd
minor edits

In the second example, we analyzed the larval *Drosophila* mushroom body connectome \citep{Eichler141762}, which has been studied as a GRDPG by \citet{athreya2020estimation}. 
This dataset consists of two graphs representing two networks of neurons, one for each hemisphere of the *Drosophila* brain. 
In these graphs, each vertex is a neuron, and the labels correspond to one of four neuron types (Kenyon Cells, Input Neurons, Output Neurons, and Projection Neurons). 
The resulting graphs are illustrated in figure \ref{fig:mbconnectome-graph}.

@@

When analyzed as a GRDPG, the ASE of each hemisphere suggests that nodes of each type falls along a curve in the latent space (figure \ref{fig:mbconnectome-ase}). 
This matches observations by \citet{athreya2020estimation}. 
In our analysis, we set the embedding dimension to $d = 4$, with 3 assortative dimensions and 1 disassortative dimension. 
We fit three latent structure Bezier curves, one for Kenyon Cells, one for Input and Output Neurons, and one for Projection Neurons, to the embedding for each hemisphere.
Then we fit a Beta distribution to to the timepoints along each curve and extracted the two Beta parameter estimates (via likelihood maximization) for each curve. 
If these Beta parameters are informative, we would expect the parameters for each hemisphere to match by neuron type, which is what we observe in these data (fig \ref{fig:mbconnectome-beta}).

>>>>

In the second example, we analyzed the larval *Drosophila* mushroom body connectome \citep{Eichler141762}, which has been studied as a GRDPG by \citet{athreya2020estimation}. 
This dataset consists of two graphs representing two networks of neurons, one for each hemisphere of the *Drosophila* brain. 
In these graphs, each vertex is a neuron, and the labels correspond to one of four neuron types (Kenyon Cells, Input Neurons, Output Neurons, and Projection Neurons). 
The number of neurons in each hemisphere is not equal (209 in the left hemisphere and 213 in the right hemisphere).
The resulting graphs are illustrated in figure \ref{fig:mbconnectome-graph}.

@@

When analyzed as a GRDPG, the ASE of each hemisphere suggests that nodes of each type falls along a curve in the latent space (figure \ref{fig:mbconnectome-ase}). 
In our analysis, we set the embedding dimension to $d = 4$, with 3 assortative dimensions and 1 disassortative dimension, and the figure only shows the first two assortative dimensions. 
This matches observations by \citet{athreya2020estimation}. 
We fit three latent structure Bezier curves, one for Kenyon Cells, one for Input and Output Neurons, and one for Projection Neurons, to the embedding for each hemisphere.
Then we fit a Beta distribution to to the timepoints along each curve and extracted the two Beta parameter estimates (via likelihood maximization) for each curve. 
If these Beta parameters are informative, we would expect the parameters for each hemisphere to match by neuron type, which is what we observe in these data (fig \ref{fig:mbconnectome-beta}).

### 2024-03-22 draft.tex
minor edits

In the second example, we analyzed the larval \emph{Drosophila} mushroom
body connectome \citep{Eichler141762}, which has been studied as a GRDPG
by \citet{athreya2020estimation}. This dataset consists of two graphs
representing two networks of neurons, one for each hemisphere of the
\emph{Drosophila} brain. In these graphs, each vertex is a neuron, and
the labels correspond to one of four neuron types (Kenyon Cells, Input
Neurons, Output Neurons, and Projection Neurons). The resulting graphs
are illustrated in figure \ref{fig:mbconnectome-graph}.

@@

When analyzed as a GRDPG, the ASE of each hemisphere suggests that nodes
of each type falls along a curve in the latent space (figure
\ref{fig:mbconnectome-ase}). This matches observations by
\citet{athreya2020estimation}. In our analysis, we set the embedding
dimension to \(d = 4\), with 3 assortative dimensions and 1
disassortative dimension. We fit three latent structure Bezier curves,
one for Kenyon Cells, one for Input and Output Neurons, and one for
Projection Neurons, to the embedding for each hemisphere. Then we fit a
Beta distribution to to the timepoints along each curve and extracted
the two Beta parameter estimates (via likelihood maximization) for each
curve. If these Beta parameters are informative, we would expect the
parameters for each hemisphere to match by neuron type, which is what we
observe in these data (fig \ref{fig:mbconnectome-beta}).

>>>>

In the second example, we analyzed the larval \emph{Drosophila} mushroom
body connectome \citep{Eichler141762}, which has been studied as a GRDPG
by \citet{athreya2020estimation}. This dataset consists of two graphs
representing two networks of neurons, one for each hemisphere of the
\emph{Drosophila} brain. In these graphs, each vertex is a neuron, and
the labels correspond to one of four neuron types (Kenyon Cells, Input
Neurons, Output Neurons, and Projection Neurons). The number of neurons
in each hemisphere is not equal (209 in the left hemisphere and 213 in
the right hemisphere). The resulting graphs are illustrated in figure
\ref{fig:mbconnectome-graph}.

@@

When analyzed as a GRDPG, the ASE of each hemisphere suggests that nodes
of each type falls along a curve in the latent space (figure
\ref{fig:mbconnectome-ase}). In our analysis, we set the embedding
dimension to \(d = 4\), with 3 assortative dimensions and 1
disassortative dimension, and the figure only shows the first two
assortative dimensions. This matches observations by
\citet{athreya2020estimation}. We fit three latent structure Bezier
curves, one for Kenyon Cells, one for Input and Output Neurons, and one
for Projection Neurons, to the embedding for each hemisphere. Then we
fit a Beta distribution to to the timepoints along each curve and
extracted the two Beta parameter estimates (via likelihood maximization)
for each curve. If these Beta parameters are informative, we would
expect the parameters for each hemisphere to match by neuron type, which
is what we observe in these data (fig \ref{fig:mbconnectome-beta}).
